Model

### 2019-10-16 stats/model.Rmd
update model code

  query.add(["pragmaticModelPredictions","parameterFree", row.condition, row.familiarObject, row.subid], [row.age, Math.exp(pragModelPredictions.score(1))])

@@

  query.add(["pragmaticModelPredictions","noise", row.condition, row.familiarObject, row.subid], [row.age, Math.exp(noisyPragModelPredictions.score(1))])

@@

@@

Infer({model,
      samples: 100,
      burn: 100,
      verbose: T,
      lag: 1,
      verboseLag: 5000,
      method: "incrementalMH",
      onlyMAP: true,
      callbacks: [callback]});
'
```

@@

```{r}
sem_know_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, sem_subj_str , sep='\n'),
  data = list(data = me_model_data, comb_data = data_comb_log),
  data_var = "dataFromR",
  model_var = "model",
  chains = 4,
  cores = 4,
  packages = c("utils/webppl-sample-writer")
)

#saveRDS(sem_know_model, "../saves/sem_know_model_variant3_100k_model_comparison_noise.rds")

sem_know_model <- readRDS("../saves/sem_know_model_variant3_200k_model_comparison_noise.rds")

model <- bind_rows(
  read_csv("../saves/model/samples126.csv")%>%mutate(chain = 1),
  read_csv("../saves/model/samples551.csv")%>%mutate(chain = 2),
  read_csv("../saves/model/samples661.csv")%>%mutate(chain = 3),
  read_csv("../saves/model/samples950.csv")%>%mutate(chain = 4)
)

@@

```{r}
log_like <- model %>%
  filter(a == "log_like")%>%
  select(-f, -d, -g, -h)%>%
  rename(type = a, 
         model =b,
         parameter = c, 
         log_like = e)%>%
  mutate(log_like = as.numeric(log_like))

@@

# model_pred <- sem_know_model %>%
#   separate(Parameter, into = c("type", "item","x"))%>%
#   filter(type == "modelPrediction")%>%
#   separate(value, into = c("age", "pred"),sep = ", ")%>%
#   mutate(age = as.numeric(str_remove_all(age, "[(c]")),
#          pred = as.numeric(str_remove(pred, "[)]")))%>%
#   select(-x)

@@

>>>>

@@

@@

    query.add(["modelPrediction","pragmatic","noise", row.condition, row.familiarObject, row.subid], [row.age, Math.exp(noisyPragModelPredictions.score(1))])

  query.add(["modelPrediction","pragmatic","free", row.condition, row.familiarObject, row.subid], [row.age, Math.exp(pragModelPredictions.score(1))])

  query.add(["modelPrediction","globalPrag","free", row.condition, row.familiarObject, row.subid], [row.age, Math.exp(globalPragModelPredictions.score(1))])

  query.add(["modelPrediction","globalPrag","noise", row.condition, row.familiarObject, row.subid], [row.age, Math.exp(noisyGlobalPragModelPredictions.score(1))])

@@

Infer({model,
      samples: 10,
      burn: 10,
      verbose: T,
      lag: 4,
      verboseLag: 5000,
      method: "incrementalMH",
      onlyMAP: true,
      callbacks: [callback]});
'
```

@@

```{r}
sem_know_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, sem_subj_str , sep='\n'),
  data = list(data = me_model_data, comb_data = data_comb_log),
  data_var = "dataFromR",
  model_var = "model",
  chains = 4,
  cores = 4,
  packages = c("webppl_packages/webppl-sample-writer")
)

#saveRDS(sem_know_model, "../saves/model1.rds")

sem_know_model <- readRDS("../saves/model1.rds")
```

@@

```{r}
log_like <- sem_know_model %>%
  separate(Parameter, into = c("parameter", "model","noise","alignment"), sep = ",")%>%
  filter(parameter == "log_like")%>%
  separate(value, into = c("na", "log_like"),sep = ",")%>%
  select(-na, -alignment)%>%
  mutate(log_like =as.numeric(str_remove(log_like,"[)]")))

@@

model_pred <- sem_know_model %>%
  separate(Parameter, into = c("type", "model","parameter","alignment","item"))%>%
  filter(type == "modelPrediction")%>%
  separate(value, into = c("age", "pred"),sep = ", ")%>%
  mutate(age = as.numeric(str_remove_all(age, "[(c]")),
         pred = as.numeric(str_remove(pred, "[)]")))

@@

plot_model_pred <- model_pred%>%
  mutate(model = paste(model, parameter, sep = "_"))%>%
  group_by(model, alignment, item, age)%>%
  summarise(mean = estimate_mode(pred),
            ci_lower = hdi_lower(pred),
            ci_upper = hdi_upper(pred))

ggplot() +
  geom_hline(yintercept = 0.5, lty=2)+
  #geom_smooth(data = data_comb_plot, aes(x = age_num, y = correct), col = "black", method = "loess", se = T, alpha = .5, span = 2)+
  geom_line(data = plot_model_pred, aes(x=age+2,y = mean, col = model), size = 1)+
  geom_ribbon(data = plot_model_pred, aes(x = age+2, ymin = ci_lower, ymax = ci_upper, fill = model), alpha = .4) +
  labs(x="Age",y="Mutual Exclusivity effect")+
  facet_grid(alignment~item)+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F, fill = F)+ 
  scale_colour_ptol(name = NULL)+
  scale_fill_ptol(name = NULL)
```

## Correlate model predictions

```{r}
binnned_data <- data_comb%>%
  group_by(subage, alignment, item)%>%
  summarize(k = sum(correct), n = n())%>%
  ungroup() %>%
  mutate(a = 1 + k,
         b = 1 + n - k,
         data_mean = (a-1)/(a+b-2),
         data_ci_lower  = qbeta(.025, a, b),
         data_ci_upper = qbeta(.975, a, b),
         age = factor(subage))%>%
  select(-a,-b,-n,-k)

cor_model_pred <- model_pred%>%
  mutate(model = paste(model, parameter, sep = "_"))%>%
  mutate(age = as.numeric(age) + min(me_data$age_num),
         age = cut(age, 
                      breaks = c(2,3,4,5),
                      labels = c(2,3,4)))%>%
  group_by(model, alignment, item, age)%>%
  summarise(model_mean = estimate_mode(pred),
            model_ci_lower = hdi_lower(pred),
            model_ci_upper = hdi_upper(pred))

plot_cor_model_pred <- cor_model_pred %>%
  left_join(
    bind_rows(
      binnned_data%>%mutate(model = "globalPrag_free"),
      binnned_data%>%mutate(model = "globalPrag_noise"),
      binnned_data%>%mutate(model = "pragmatic_free"),
      binnned_data%>%mutate(model = "pragmatic_noise")
      )
  )

ggplot(data = plot_cor_model_pred,aes(x = model_mean, y = data_mean, col = item)) +
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
  geom_errorbar(aes(ymin = data_ci_lower, ymax = data_ci_upper),width = 0,size = .7)+
  geom_errorbarh(aes(xmin = model_ci_lower, xmax = model_ci_upper), height = 0,size = .7)+
  geom_point(size = 1,  stroke = 1)+
  coord_fixed()+
 stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = model_mean, y = data_mean), inherit.aes = F, size = 3)+
  xlim(0,1)+ylim(0,1)+
  xlab("Model")+
  ylab("Data")+
  facet_grid(age~model)+
  theme_few() + 
  scale_colour_viridis_d(name ="Item")
```
